Measurement and Analysis of Child Pornography Trafficking on P2P Networks\nocite{Hurley}

### 2013-10-15 Paper_presentation.tex
Multirow

\documentclass[notes]{beamer}
\usepackage{graphicx}
\usepackage{url}
\usepackage[english, portuguese]{babel}
\usepackage[latin1, utf8]{inputenc}
\usepackage{times}
\usepackage[T1]{fontenc}
\usepackage{fancyhdr}
\setbeamertemplate{caption}[numbered]
\mode<presentation>

@@

>>>>

\documentclass[notes]{beamer}
\usepackage{graphicx}
\usepackage{url}
\usepackage[english, portuguese]{babel}
\usepackage[latin1, utf8]{inputenc}
\usepackage{times}
\usepackage{multirow}
\usepackage[T1]{fontenc}
\usepackage{fancyhdr}
\setbeamertemplate{caption}[numbered]
\mode<presentation>

@@

\caption{Characterization of GUIDs groups} 
\label{tab:table4}
\begin{tabular}{c|ccc}\hline & \multicolumn{1}{c}{GUID Groups} & \multicolumn{2}{c}{Mean Value (99\% CI)} \\

\hline 
& & Corpus Size & Days Observed \\

\hline
\hline
\parbox[t]{2mm}{\multirow{6}{*}{\rotatebox[origin=c]{90}{Gnutella}}} & All & 10.9 (10.7, 11.1) & 5.2 (5.2, 5.2) \\
& TOR & 43.9 (39.0, 49.6) & 23.4 (21.8, 25.1)\\
& Relayed & 18.9 (18.3, 19.5) & 4.8 (4.7, 4.9)\\
& Multi-Network & 25.9 (24.9, 27.0) & 10.8 (10.6, 11.0)\\
& Top 10\% Obs. & 41.8 (40.7, 43.0) & 28.7 (28.5, 29.0)\\
& Top 10\% Corp. & 75.9 (74.3, 77.7) & 16.2 (16.0, 16.5)\\
& Top 10\% Contr. & 69.1 (67.6, 70.9) & 19.5 (19.3, 19.8)\\
\hline
